&nbsp;

```{r include = FALSE}
library(dplyr)
library(kableExtra)

avail_images_info <- rbind(c("postal", "normalized and parsed addresses"),
                           c("geocoder", "geocode"),
                           c("census_block_group", "census block group and tract"),
                           c("st_census_tract", "spatiotemporal census tract 1970 - 2020"),
                           c("dep_index", "census tract-level deprivation index"),
                           c("roads", "proximity and length of major roads"),
                           c("aadt", "average annual daily traffic"),
                           c("greenspace", "enhanced vegetation index"),
                           c("nlcd", "land cover (imperviousness, land use, greenness)"),
                           c("pm", "daily PM2.5"),
                           c("narr", "daily weather data (temperature, humidity, etc)"),
                           c("drivetime", "distance and drive time to care sites"),
                           c("h3", "h3 hierarchical spatial index	")) %>%
  as_tibble() %>%
  setNames(c("degauss_name", "desc"))

images_table <- tibble(image = glue::glue("[`ghcr.io/degauss-org/{avail_images_info$degauss_name}`]",
                                          "(https://degauss.org/{avail_images_info$degauss_name})"),
                       description = avail_images_info$desc,
                       version = glue::glue(
                         "[![](https://img.shields.io/github/v/release/degauss-org/{avail_images_info$degauss_name}",
                         "?color=C2326B&label=version&sort=semver)]",
                         "(https://github.com/degauss-org/{avail_images_info$degauss_name}/releases)"
                       ))
```


To get started finding the right DeGAUSS image for your project, try using our [menu](http://app.degauss.org/menu/).

```{r echo = FALSE}
knitr::kable(images_table, 
             col.names = c("image*", "description", "version**"),
             align = "lcc") %>%
  kable_styling(full_width = T) %>%
  column_spec(3, width = "25%")
```

**\*** Recent versions of DeGAUSS containers are hosted on the GitHub Container Registry and now require the `ghcr.io` prefix in a [DeGAUSS command](using_degauss.html#DeGAUSS_Commands) to specify this. Older DeGAUSS images were hosted on [Docker Hub](https://hub.docker.com/u/degauss) and many are still available there. 

**\*\*** The badges display the most recent version of each DeGAUSS image. Click the badge to visit the GitHub releases page with notes about changes made in each version. When running a DeGAUSS container image, it is possible to specify an older version by changing the tag at the end of the repo/image name, e.g. `ghcr.io/degauss-org/geocoder:3.0.1`.


